title

### 2013-02-04 paper.tex
State clustering added

@@

Our modelling of future water needs is consistent with external research
on drought locations\cite{key-13}, in that it suggests many of the
areas at risk of drought do not have the proximity to water sources
required to make the construction of de-salinization plants feasible.

>>>>

\section{Meeting Local Demands}

Although the total demand is projected to increase by about $2\%$ across the United States, most of this usage increase is concentrated in a few areas. By state, the most dramatic projected increases in water usage occur in the following regions: South Florida, Arkansas and Missouri, Nebraska, Wyoming and Colorado, and California and Arizona (See Figure). Such substantial and permanent increase in water usage requires permanent increases in supply.

To solve this problem, we propose to strategically place desalination plants in the coastal regions, namely California and Florida, that require water and build reservoirs to serve inland regions, namely the Arkansas and Nebraska regions.

@@

Our modeling of future water needs is consistent with external research
on drought locations\cite{key-13}, in that it suggests many of the
areas at risk of drought do not have the proximity to water sources
required to make the construction of de-salinization plants feasible.
